\newpage
\begin{small}
    \begin{center}
    \begin{minipage}{0.4\paperwidth}
        \section*{Colophon \& Copyright}
        This document was typeset using \LuaTeX%
        \footnote{%
        \TeX\ is
        a typesetting software, free and open source,
        developed by Donald Knuth. \LaTeX\ is a macro
        set for \TeX\ developed by Leslie Lamport. \LuaTeX\ is
        a reworking of \TeX\ adding native support for the Lua
        programming language and unicode, among other things.
        All of them are available in all major
        operating systems.
        }
        and the \LaTeXe\ macros in a Linux operating system.
        The editor used for editing the text was Kile%
        \footnote{
        Kile is an editor from the KDE project,
        that offers good integration with \LaTeX\
        and an experience close to an IDE.
        It is free and open source and easily
        obtainable in UNIX like operating systems
        and (I believe) MS Windows.
        The KDE project is a huge software project
        aiming at providing a cohesive desktop experience
        in UNIX like operating systems (mostly linux).
        }.
        The main typefaces used are Charis SIL%
        \footnote{
        A slight rework of the Charter
        typeface by Mathew Carter
        with extended language support and many,
        many, more glyphs.
        }
        for text with Go%
        \footnote{
        Designed by Bigelow \& Holmes for the
        Go programming language.
        }
        for sans-serif
        and XITS for maths%
        \footnote{%
        In \LuaLaTeX\ this amounts to using the package
        \icode{unicode-math}
        and then setting the corresponding
        opentype fonts}.

        \medskip
%         \begin{quote}
        \begin{quote}\sffamily\raggedright
        E-mail: \url{jalb97@gmail.com} \\
        Copyright Jhonny Lanzuisi 2021\\
        This work is licensed under the Creative Commons Attribution-ShareAlike
        International (CC BY-SA 4.0)  License. To view a copy of the license,
        visit \url{https://creativecommons.org/licenses/by-sa/4.0/}.
        \end{quote}
%         \end{quote}
    \end{minipage}
    \end{center}
\end{small}
\newpage
\tableofcontents

